\documentclass{my_cv}
\begin {document}
\name{PAPADIMITRIOU NIKOLAOS}
\contact{9 boulevard de la Lorraine}{Lille}{France 59000}{npapadimitriou@isc.tuc.gr}{(+33)0767109446}

\contactsocialmedia{\linkedin{\href{https://www.linkedin.com/in/nikolaos-papadimitriou-1b982983/}{nikolaos-papadimitriou-1b982983}}}{\github{\href{github.com/npapadimitriou}{github.com/npapadimitriou}}}



 \section{Working Experience}
 
 \datedsubsection{\textbf{Full stack software engineer} }{05/2021 - 12/2021}
 \textit{Software Engineer at Hellenic Army Information Technology Support Center (KEPYES) Athens Greece}
 \\
 I worked on a project for the relocation of military personel using PHP,js,MySQL and Selenium.
 I also did service as a soc analyst using CheckPoint SmartView, Wazuh and Splunk (siem)

\datedsubsection{\textbf{Web developer} }{05/2019 - 04/2020}
 \textit{Efficience It Lille France}
\\
During my work in Efficience IT I participated in four projects  .  


\workitems
{The first one was front end for a baby food manufacturer}
{The second was full stack in a CRM for an
	real estate agency.}
{The third was back-end for a full-service wholesaler product distributor supplying wholesalers and supermarkets.}
{ The last one was full stack for a job search engine.}

Technologies that were used
\\
Symfony 4, php, HTML, javascript, JQUERY, BOOTSTRAP,CSS ELASTIC SEARCH,DOCKER
GIT, NGINX Curl, DOCTRINE QueryBuilder
cronjobs REST/JSON API)

\datedsubsection{\textbf{Robotics software developer} }{01/12/2017 - 31/03/2018}
\textit{Inria FUN team  Villeneuve D 'Ascq, France}
\\
I was part of FUN team in the set up of a demonstrator staging a scenario for illustrating the research result of a phd student. This demonstrator involved RFID
readers and tags and a fleet of mobile robots. 
\workitems
{participation in the scenario description}
{	implementation part dedicated to the mobile robots(turtlebots)}
{train on robotic OS (ROS)
	but also in distributed computing}
{autonomous movement , communication and mapping (slam) }

Technologies that were used
\\
C++, Java, Python, ROS, Rfid

\datedsubsection{\textbf{Automation Engineer} }{07/2016 - 08/2016}
\textit{D.E.Y.A.X. (Municipal Enterprise for Water and Sewage of Chania)  Chania,  Greece}
\\
\begin{itemize}
	\item Manage / monitor motors (PLC, Scada)
	\item Practical challenges (installation / replacement / calibration of sensors, starter repair)

\end{itemize}%

\datedsubsection{\textbf{Reseller} }{01/2010 - 09/2017}
\textit{Stymtime  Chania,  Greece}
\\
Reseller at my family business​ which deals with selling Watches and Watch
batteries. I had to communicate with the customers  in person , present and
provide the merchandise .


\section{Education}
\datedsubsection{Technical University of Crete}{2009--2017}
During my studies I get involved with a great variety of technologies as my university school
has a double field direction. I got skills in collaboration ,
project management and also I developed a strong theoretical background.


\studyitems
{electronics}
{automatic control systems}
{computer science}
{telecommunications}

	
\subsection{\underline{Master Thesis}}
\textbf {\large{Cloud-based virtual building management system}}
supervised by Mr. Kalaitzakis Konstantinos
\\
\\
The object of the thesis was to create a web application  that will manage the
devices of a university laboratory as long as their data and extracts information
using fuzzy logic algorithms. The projects was based on the hardware agnostic
platform openHAB and the technologies that were used are : Xtext, lua, matlab,
html, javascript, css, bootstrap,php.	
	
 	\section{Skills}
 	\begin{tabular}{l l l l}
 		C/C++ & Python & Javascript & PHP \\
 		GIT & Matlab & CSS/Bootstrap & VHDL\\
 		Symfony & ROS & LUA & Latex
 	\end{tabular}
 
\section{Languages}
Greek mother tongue\\ English  Cambridge B2\\ French DEFL B1  
\end{document}



